### 2019-02-02 Seneca.tex
chandras pass

We assume that the dataset supplied to Seneca by the user
is representative of datasets on which the 
resulting model will be use.  In addition, we use prediction error as the 
score (i.e., mean squared error for regression and accuracy percentage for classification) 
instead of $R^2$, which describes explanatory power, to avoid overfitting.
As part of future work, we are considering using multiple datasets and a ranges
of hyperparameter values (versus lists) to preclude the need for users to specify
them and to consider a wider range of possible values.

>>>>

We assume that the dataset supplied to Seneca by the user
is representative of datasets on which the 
resulting model will be use.  In addition, we use prediction error as the 
score (i.e., mean squared error for regression and accuracy percentage for classification) 
instead of $R^2$, which describes explanatory power, to avoid overfitting.
As part of future work, we are considering using multiple datasets and a ranges
of hyperparameter values (versus lists) to preclude the need for users to specify
them and to consider a wider range of values.

### 2019-02-02 conclusion.tex
chandras pass

In this paper, we present Seneca, a new framework for simplifying and expediting
the training and testing of machine learning models in terms of their prediction 
power using very low cost cloud computing services.
Specifically, Seneca leverages the AWS Lambda serverless cloud service for autoscaled
(elastic) and parallel execution of hyperparameter search and selection for machine learning
applications.  
Users provide Seneca with the application code and libraries, 1+ datasets, and the list 
of possible hyperparameter settings.  Seneca uses this 
information to automatically construct an AWS Lambda function that
that invokes the application, imports and splits the dataset into training
and testing datasets, and constructs, tests, and evaluates (i.e. scores) a machine
learning model for a particular configuration of hyperparameter settings.  
Seneca orchestrates parallel execution of these functions for all possible 
combinations of hyperparameter values specified and returns the best scoring model
and configuration to the user (for future use on other datasets).

>>>>

We present a new framework, called Seneca, for simplifying and expediting
the training and testing of machine learning models
using low cost cloud services.
Specifically, Seneca leverages the AWS Lambda for autoscaled
(elastic) and parallel execution of hyperparameter search 
and selection for machine learning models.  
Users provide Seneca with the application code and libraries, 1+ datasets, and the list 
of possible hyperparameter settings.  
%Seneca uses this 
%information to automatically construct models using parallel functions in AWS Lambda. 
%an AWS Lambda function that
%that invokes the application, imports and splits the dataset into training
%and testing datasets, and constructs, tests, and evaluates (i.e. scores) a machine
%learning model for a particular configuration of hyperparameter settings.  
Seneca uses this information to orchestrate parallel execution of these functions for all possible 
combinations of hyperparameter values specified and returns the best scoring model
and configuration to the user (for future use on other datasets).

### 2019-02-02 related_work.tex
chandras pass

Multiple researchers have investigated the efficacy and overhead of the
serverless programming model and implementations.
the benefit and drawback of such has been well researched by
The authors in \cite{ref:onesteptwostep} evaluates the cost and performance of using
serverless for data-intensive computing.  They identify some key weaknesses in AWS
Lambda for this application domain including the inability to effectively train models.
Our work show that it is possible for a subset of machine learning applications to 
train models in a cost effective ways.
\cite{ref:baldini2017} identifies multiple open research questions surrounding serverless,
including whether or not functions should be stateless. 
%please also discuss and cite these papers - you may need a second paragraph
%http://www.cs.ucsb.edu/~ckrintz/papers/ic2e18.pdf
%http://shivaram.org/publications/pywren-socc17.pdf
%S. Fouladi, R. S. Wahby, B. Shacklett, K. V. Balasubramaniam, W. Zeng, R. Bhalerao, A. Sivaraman, G. Porter, and K., Winstein. “Encoding, Fast and Slow: Low-Latency Video Pro- cessing Using Thousands of Tiny Threads”. In: NSDI. Boston, MA: USENIX Association, 2017, pp. 363–376.
%A. Klimovic, Y. Wang, C. Kozyrakis, P. Stuedi, J. Pfefferle, and A. Trivedi. “Understanding Ephemeral Storage for Serverless Analytics”. In: USENIX ATC. Boston, MA: USENIX Associa- tion, 2018, pp. 789–794.
%. Wang, M. Li, Y. Zhang, T. Ristenpart, and M. Swift. “Peek- ing Behind the Curtains of Serverless Platforms”. In: USENIX ATC. Boston, MA: USENIX Association, 2018, pp. 133–146.

The serverless framework~\cite{ref:serverless_framework} contributes an 
automated packaging and deployment toolseet for serverless functions across clouds. 
The serverless framework uses Cloudformation~\cite{ref:cloudformation} to package and deploy Lambda function, which introduces additional cost. Seneca uses local docker container to avoid this cost
and overhead. The cloud infrastructure provisioning framework Terraform~\cite{ref:terraform} 
also provides automated deployment of functions to serverless platforms, but it does not simulate the AWS Lamdba runtime to create the deployment package (doing so on a non-Linux system will result in Lambda errors and failures at execution time). 
In addition, AWS CodeDeploy~\cite{ref:codedeploy} serves as component in the continuous integration and delivery pipeline for serverless architectures, but it also introduces monetary cost overhead
to do so.

>>>>

Multiple researchers have investigated the efficacy and overhead of the
serverless programming model and 
implementations~\cite{ref:baldini2017,ref:jonas2017occupy,ref:onesteptwostep,ref:lin2018tracking}.
The authors in \cite{ref:onesteptwostep} evaluates the cost and performance of using
serverless for data-intensive computing.  They identify some key weaknesses in AWS
Lambda for this application domain including the inability to effectively train models.
Our work show that it is possible for the subset of machine learning applications that we 
consider, to train models in a cost effective ways.

%\cite{ref:baldini2017} identifies multiple open research questions surrounding serverless,
%including whether or not functions should be stateless. PyWren~\cite{ref:jonas2017occupy} provides us 
a new perspective of stateless function being a natural fit for distributed computing models, because it 
abstracts away cluster management overhead and is ideal for embarrassingly parallel jobs. 
ExCamera~\cite{ref:encoding} presents a 
framework for running general-purpose parallel tasks (encoding 4K video) 
on a commercial serverless platform using multithreading. 
An empirical comparison of resource utilization and performance isolation
is provided in~\cite{ref:peeking} for AWS Lambda, 
Azure Functions, and Google Cloud Functions.
%to discuss the resource utilization and performance isolation efficiency of 
%three platforms. Besides efficacy and efficiency, there are challenges serverless architecture are facing in terms of 
%application monitoring and distributed storage. GammaRay~\cite{ref:lin2018tracking} proposes a cloud service that extracts
%causal dependencies across serverless functions and cloud services without programmer intervention. Such monitoring and 
%debugging tool simplifies the development and maintenance of serverless applications. Pocket~\cite{ref:ephemeral} provides 
%an elastic and economical distributed data store for severless analytic applications. We expect more contributions to toolchain 
%and distributed storage of serverless in upcoming years.

%please also discuss and cite these papers - you may need a second paragraph
%http://www.cs.ucsb.edu/~ckrintz/papers/ic2e18.pdf
%http://shivaram.org/publications/pywren-socc17.pdf
%S. Fouladi, R. S. Wahby, B. Shacklett, K. V. Balasubramaniam, W. Zeng, R. Bhalerao, A. Sivaraman, G. Porter, and K., Winstein. “Encoding, Fast and Slow: Low-Latency Video Pro- cessing Using Thousands of Tiny Threads”. In: NSDI. Boston, MA: USENIX Association, 2017, pp. 363–376.
%A. Klimovic, Y. Wang, C. Kozyrakis, P. Stuedi, J. Pfefferle, and A. Trivedi. “Understanding Ephemeral Storage for Serverless Analytics”. In: USENIX ATC. Boston, MA: USENIX Associa- tion, 2018, pp. 789–794.
%. Wang, M. Li, Y. Zhang, T. Ristenpart, and M. Swift. “Peek- ing Behind the Curtains of Serverless Platforms”. In: USENIX ATC. Boston, MA: USENIX Association, 2018, pp. 133–146.

The serverless framework~\cite{ref:serverless_framework} contributes an 
automated packaging and deployment toolset for serverless functions across clouds. 
The serverless framework uses Cloudformation~\cite{ref:cloudformation} to package and deploy Lambda function, which introduces additional cost. Seneca uses local docker container to avoid this cost
and overhead. The cloud infrastructure provisioning framework Terraform~\cite{ref:terraform} 
also provides automated deployment of functions to serverless platforms, but it does not simulate the AWS Lamdba runtime to create the deployment package (doing so on a non-Linux system will result in Lambda errors and failures at execution time). 
In addition, AWS CodeDeploy~\cite{ref:codedeploy} serves as component in the continuous integration and delivery pipeline for serverless architectures, but it also introduces monetary cost overhead
to do so.

### 2019-02-02 results.tex
chandras pass

\begin{figure}[t] \centering 
\vspace{-0.2in}
\includegraphics[scale=0.36]{box_plot_mse_2}
\vspace{-0.2in}
\caption{The box plot of MSE metric from three regression applications in the entire hyperparameter tuning search space. The red notch shows the MSE from the default settings. The colored diamonds are outliers beyond two interquartile ranges. Lower MSE values are better.
\label{fig:box_plot_mse}}
\vspace{-0.2in}
\end{figure}

%using the three regression applications: 
%Prophet, Multi-Regression, and XGBoost (regression task). 
Table~\ref{tab:mse} shows the effect of Seneca on the quality of the
regressions generated by Prophet, Multi-regression, and XGBoost (when used as
a regression algorithm). The first row of the table indicates the number of
different hyperparameter settings Senica considered.  Rows 3 through 5 show
the MSE generated by the default hytperparameter settings, the best (lowest
MSE) Seneca was able to find, and the worst (largest MSE) that Seneca tested
for each regression algorithm and dataset.

@@

The 80-20 case represents the typical usage of these classification
applications.  Often, when evaluating the accuracy of a specific classifier,
the user uses the 80-20 split ``rule'' when measuring accuracy.  In this case,
Seneca's improvement over the default parameterizations varies from less than
1\% for the Neural Network (NN) application (column 4 for 80-20), to 61.5\% for SVC
(best versus default in column 3 for 80-20 in the table).

>>>>

\begin{figure}[t] \centering 
\vspace{-0.2in}
\includegraphics[scale=0.36]{box_plot_mse_2}
\vspace{-0.4in}
\caption{The box plot of MSE metric from three regression applications in the entire hyperparameter tuning search space. The red notch shows the MSE from the default settings. The colored diamonds are outliers beyond two interquartile ranges. Lower MSE values are better.
\label{fig:box_plot_mse}}
\vspace{-0.2in}
\end{figure}

%using the three regression applications: 
%Prophet, Multi-Regression, and XGBoost (regression task). 
Table~\ref{tab:mse} shows the effect of Seneca on the quality of the
regressions generated by Prophet, Multi-regression, and XGBoost (when used as
a regression algorithm). The first row indicates the number of
different hyperparameter settings Senica considered.  Rows 3 through 5 show
the MSE generated by the default hyperparameter settings, the best (lowest
MSE) Seneca was able to find, and the worst (largest MSE) that Seneca tested
for each regression algorithm and dataset.

@@

The 80-20 case represents the typical usage of these classification
applications.  Often, when evaluating the accuracy of a specific classifier,
the user uses the 80-20 split ``rule'' when measuring accuracy.  In this case,
Seneca's improvement over the default parameterizations varies from less than
1\% for the Neural Network (NN) application (column 4), to 61.5\% for SVC
(best versus default in column 3).
